\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
cite freecad again here because it makes sense
hyph

STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface 
based on FreeCAD. FreeCAD is an open source CAD/CAM program, which 
in turn is based on OpenCASCADE. FreeCAD allows for scripting in Python 
and acts as a simple to use interface to OpenCASCADE.  A STEP CAD file 
could be considered as a hierarchical tree of parts and \emph{part assemblies}, 
where a part assembly is a collection of \emph{part features}. A part feature can be used 
to create a triangular mesh which can be used to create a \PYGEOMETRY{} tessellated solid. The placement 
of the part feature is extracted from the STEP file and used to create an 
appropriate physical volume. Assignment of materials and visualisation 
attributes must be performed by  the user after conversion to GDML as rarely 
will CAD/CAM packages included the detailed information required for MCRT 
codes. Listing~\ref{lst:pythonCADLoading} shows 
how \PYGEOMETRY{} can load step files.
\begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
reader = pyg4ometry.freecad.Reader("CadFileName.step")
reader.relabelModel()
reader.convertFlat()
logical = reader.getRegistry().getWorldVolume()
\end{lstlisting}
Compared to other file readers, two additional steps are required \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model 
part names can contain characters which are not allowed in Python dictionaries so need to be replaced by \pyinline{relabelModel}. 
CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
In general there is no requirement to avoid geometric overlap  of parts in a CAD file. This will result in overlaps of the solids in 
the converted tessellated solids. This is avoided by shrinking each solid, this is done by computing the a normal ${\bf n}$  for each 
vertex ${\bf v}$ and shifting its position by $\epsilon {\bf n}$, so the new vertices are ${\bf v} - \epsilon {\bf n}$. The degree of shrinking 
is user controllable.

>>>>

STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface 
based on FreeCAD~\cite{FreeCAD}. FreeCAD is an open source CAD/CAM program, which 
in turn is based on OpenCASCADE. FreeCAD allows for scripting in Python 
and acts as a simple-to-use interface to OpenCASCADE.  A STEP CAD file 
could be considered as a hierarchical tree of parts and \emph{part assemblies}, 
where a part assembly is a collection of \emph{part features}. A part feature can be used 
to create a triangular mesh which can be used to create a \PYGEOMETRY{} tessellated solid. The placement 
of the part feature is extracted from the STEP file and used to create an 
appropriate physical volume. Assignment of materials and visualisation 
attributes must be performed by  the user after conversion to GDML as rarely 
will CAD/CAM packages included the detailed information required for MCRT 
codes. Listing~\ref{lst:pythonCADLoading} shows 
how \PYGEOMETRY{} can load step files.
\begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
reader = pyg4ometry.freecad.Reader("CadFileName.step")
reader.relabelModel()
reader.convertFlat()
logical = reader.getRegistry().getWorldVolume()
\end{lstlisting}
Compared to other file readers, two additional steps are required \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model 
part names can contain characters which are not allowed in Python dictionaries so need to be replaced by \pyinline{relabelModel}. 
CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
In general there is no requirement to avoid geometric overlap  of parts in a CAD file. This will result in overlaps of the solids in 
the converted tessellated solids. This is avoided by shrinking each solid, this is done by computing the a normal ${\bf n}$  for each 
vertex ${\bf v}$ and shifting its position by $\epsilon {\bf n}$, so the new vertices are ${\bf v} - \epsilon {\bf n}$. The degree of shrinking 
is user controllable.
